Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-24 paper/paper.tex
small changes to paper

We model $Y$ as a Normal distribution 
\begin{align}
Y \sim N(\mu, \sigma_{1}^2)
\end{align}
where $\mu$ and $\sigma_{1}^2$ are the average similarity score and the variance
of similarity scores of all pairs of items, respectively. Since $X_n$ represents
a noisy reading of the true similarity $Y$, we model $X_n | Y$ as a Normal
distribution around $Y$:
\begin{align}
(X_n | Y=y) \sim N(y, \sigma_{2, n}^2)
\end{align}

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.5\textwidth]{twonormals.png}
	\caption{The blue curve represents $Y$, the distribution of true
    similarities between a random pair of items. The red curve represents $X|Y$,
    the estimated similarity when a small number of common users exist.}
    \label{fig:two_normals}
\end{figure}

>>>>

We model $Y$ as a Normal distribution 
\begin{align}
Y \sim N(\mu, \sigma_{1}^2)
\end{align}
where $\mu$ and $\sigma_{1}^2$ are the average similarity score and the variance
of similarity scores of all pairs of items, respectively. Since $X_n$ represents
a noisy reading of the true similarity $Y$, we model $X_n | Y$ as a Gaussian
error around $Y$:
\begin{align}
(X_n | Y=y) \sim N(y, \sigma_{2, n}^2)
\end{align}

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.5\textwidth]{twonormals.png}
	\caption{The blue curve represents $Y$, the distribution of true
    similarities between a random pair of items. The red curve represents $X|Y$,
    the observed similarity when a small number of common users exist.}
    \label{fig:two_normals}
\end{figure}
